---
output: rmarkdown::github_document
---

# BensThemes

[![GitHub license](https://img.shields.io/github/license/Naereen/StrapDown.js.svg)](https://github.com/Naereen/StrapDown.js/blob/master/LICENSE)

A package for R that contains the custom themes I use for ggplot2. This was made for my own personal use but if you would also like to use these themes follow the steps below.
 
## Installation
 
This project is not on CRAN so to download you will need to have the package devtools for R.
 
```R
devtools::install_github("benchaffe/BensThemes")
```
 
To use the fonts you may also need the package extrafont. Simply follow the steps below.
 
```R
library(extrafont)
font_import()
loadfonts(device = "win")
```

`font_import()` can take around 5 minutes.

## Themes

- ```theme_belightgray``` A modern light gray theme.
- ```theme_bedark``` A modern dark theme.
- ```theme_bedarkish``` This is a lighter dark theme.

## Examples


```{r message=FALSE, echo=FALSE, error=FALSE}
library(ggplot2)
library(BensThemes)
library(extrafont)
```


Note: all themes have the option `axisLabels = FALSE` by default. Simply set to true like the examples above to see them.

### Light Gray Theme

```{r lg}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(title = "Scatterplot of mtcars data", 
       subtitle = "An example subtitle", 
       caption = "BensThemes") +
  theme_belightgray(axisLabels = TRUE)
```

### Dark Theme

```{r d}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point(color = rgb(255, 235, 30, maxColorValue = 255, alpha = 255)) +
  labs(title = "Scatterplot of mtcars data",
       subtitle = "An example subtitle",
       caption = "BensThemes") +
  theme_bedark(axisLabels = TRUE)
```

### Dark-ish Theme

```{r di}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point(color = rgb(255, 235, 30, maxColorValue = 255, alpha = 255)) +
  labs(title = "Scatterplot of mtcars data",
       subtitle = "An example subtitle",
       caption = "BensThemes") +
  theme_bedarkish(axisLabels = TRUE)
```
